Analysis

### 2022-06-15 production/prod_analysis-fix-t5.Rmd
update ola cateogorica y % migrant

---
title: "Preparación de datos"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
      number_sections: yes
    code_folding: hide
    number_sections: yes
editor_options:
  chunk_output_type: console
---
# Setup

@@

```{css, echo=FALSE}
# /* expandir el espacio del documento*/
body .main-container {
      max-width: 1600px !important;
      width: 1600px !important;
    }
#/* expandir width de la TOC*/
div.tocify {
    width: 22% !important;
    max-width: 331px !important;
    max-height: 102% !important;
}
```

@@

```{r tab-desc, results="asis", warning=FALSE}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# Css
st_css()
st_options(lang = "en",
           footnote = NA,
           bootstrap.css = F,
           custom.css = here::here("input/css/dfsummary.css"),
           dfSummary.custom.1 = NA
           )

# Df variables nivel 1
# df<- dfSummary(df_study1_long %>% select(in_simpat:edad),
#                plain.ascii = FALSE,
#                style = "grid",
#                tmp.img.dir = "/tmp",
#                graph.magnif = TRUE,
#                headings = F,  # encabezado
#                varnumbers = F, # num variable
#                labels.col = T, # etiquetas
#                na.col = F,    # missing
#                graph.col = T, # plot
#                valid.col = T, # n valido
#                col.widths = c(700,10,10,10,10)
#                )
# df$Variable <- NULL # delete variable column
# view(df,
#      file = here::here("output/tables/desc01.html")
#      ) # Ver tabla en un archivo HTML
# webshot::webshot(url =here::here("output/tables/desc01.html"),
#         file =here::here("output/tables/desc01.png")) # Remover archivo HTML
# # print(df, method = "render")

# Df variables nivel 1 __________________________________________________________
df_study1 <- df_study_long_t5_comunas %>% select(in_simpat:edad,
                                                 inm_prop_cas17_w,
                                                 inm_prop_cas20_w,dif_inm) 
lab_study1 <- sjlabelled::get_label(df_study1) 
df_study1 <- df_study1 %>% na.omit() %>% sjlabelled::set_label(lab_study1)

df<- dfSummary(x = df_study1,
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = T, # n valido
               col.widths = c(700,10,10,10,10,10)
               )
# df$Variable <- NULL # delete variable column
view(df,
     file = here::here("output/tables/desc02.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/desc02.html"),
        file =here::here("output/tables/desc02.png")) # Remover archivo HTML
# print(df, method = "render")
```

@@

## A. Anxiety

```{r anxiety}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,in_simpat:edad,inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(conviviality=(in_ansied+in_simpat+in_valfam+in_valami+in_amigcl)/5,
         identity= (in_simili+in_amsimb+in_acpier+in_acadop)/4,
         threat = as.numeric(in_amreal),
         ola=as.numeric(ola)
         )
# Hipotesis
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+dif_inm+nation_t1+cuestion_mig"

# A. Anxiety (in_ansied)
anx.null <- lmer(formula(paste0("in_ansied~","1 + (1|idencuesta)+(1|comuna)")),data = df_study1)
anx1 <- lmer(formula(paste0("in_ansied~",h1,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
anx2.ed <- lmer(formula(paste0("in_ansied~",h2.educ,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
anx2.in <- lmer(formula(paste0("in_ansied~",h2.incom,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
anx3 <- lmer(formula(paste0("in_ansied~",h3,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
anx4.kno <- lmer(formula(paste0("in_ansied~",h4.know,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
anx4.fri <- lmer(formula(paste0("in_ansied~",h4.friend,"+(1|idencuesta)+(1|comuna)")),data = df_study1)

omit <- "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
texreg::knitreg(list(anx1,anx2.ed,anx2.in,anx3,anx4.fri,anx4.kno),
          omit.coef = omit)
```

## B. Simpathy

```{r simpathy}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,in_simpat:edad,inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(conviviality=(in_ansied+in_simpat+in_valfam+in_valami+in_amigcl)/5,
         identity= (in_simili+in_amsimb+in_acpier+in_acadop)/4,
         threat = as.numeric(in_amreal),
         ola=as.numeric(ola)
         )
# Hipotesis
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+dif_inm+nation_t1+cuestion_mig"

# B. Simpathy (in_simpat)
simp.null <- lmer(formula(paste0("in_simpat~","1 + (1|idencuesta)+(1|comuna)")),data = df_study1)
simp1 <- lmer(formula(paste0("in_simpat~",h1,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
simp2.ed <- lmer(formula(paste0("in_simpat~",h2.educ,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
simp2.in <- lmer(formula(paste0("in_simpat~",h2.incom,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
simp3 <- lmer(formula(paste0("in_simpat~",h3,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
simp4.kno <- lmer(formula(paste0("in_simpat~",h4.know,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
simp4.fri <- lmer(formula(paste0("in_simpat~",h4.friend,"+(1|idencuesta)+(1|comuna)")),data = df_study1)

omit <- "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
texreg::knitreg(list(simp1,simp2.ed,simp2.in,simp3,simp4.fri,simp4.kno),
          omit.coef = omit)
```

## C. Family value migrant friends

```{r family-value}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,in_simpat:edad,inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(conviviality=(in_ansied+in_simpat+in_valfam+in_valami+in_amigcl)/5,
         identity= (in_simili+in_amsimb+in_acpier+in_acadop)/4,
         threat = as.numeric(in_amreal),
         ola=as.numeric(ola)
         )
# Hipotesis
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+dif_inm+nation_t1+cuestion_mig"

# C. Family value migrant friends (in_simpat)
valfam.null <- lmer(formula(paste0("in_valfam~","1 + (1|idencuesta)+(1|comuna)")),data = df_study1)
valfam1 <- lmer(formula(paste0("in_valfam~",h1,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
valfam2.ed <- lmer(formula(paste0("in_valfam~",h2.educ,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
valfam2.in <- lmer(formula(paste0("in_valfam~",h2.incom,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
valfam3 <- lmer(formula(paste0("in_valfam~",h3,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
valfam4.kno <- lmer(formula(paste0("in_valfam~",h4.know,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
valfam4.fri <- lmer(formula(paste0("in_valfam~",h4.friend,"+(1|idencuesta)+(1|comuna)")),data = df_study1)

omit <- "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
texreg::knitreg(list(valfam1,valfam2.ed,valfam2.in,valfam3,valfam4.fri,valfam4.kno),
          omit.coef = omit)
```

## D. Friend value migrant friends

```{r friends-value}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,in_simpat:edad,inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(conviviality=(in_ansied+in_simpat+in_valfam+in_valami+in_amigcl)/5,
         identity= (in_simili+in_amsimb+in_acpier+in_acadop)/4,
         threat = as.numeric(in_amreal),
         ola=as.numeric(ola)
         )
# Hipotesis
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+dif_inm+nation_t1+cuestion_mig"

# D. Friend value migrant friends(in_simpat)
valami.null <- lmer(formula(paste0("in_valami~","1 + (1|idencuesta)+(1|comuna)")),data = df_study1)
valami1 <- lmer(formula(paste0("in_valami~",h1,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
valami2.ed <- lmer(formula(paste0("in_valami~",h2.educ,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
valami2.in <- lmer(formula(paste0("in_valami~",h2.incom,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
valami3 <- lmer(formula(paste0("in_valami~",h3,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
valami4.kno <- lmer(formula(paste0("in_valami~",h4.know,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
valami4.fri <- lmer(formula(paste0("in_valami~",h4.friend,"+(1|idencuesta)+(1|comuna)")),data = df_study1)

omit <- "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
texreg::knitreg(list(valami1,valami2.ed,valami2.in,valami3,valami4.fri,valami4.kno),
          omit.coef = omit)
```

## E. Immigrants have Chilean friends

```{r imig-clfriends}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,in_simpat:edad,inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(conviviality=(in_ansied+in_simpat+in_valfam+in_valami+in_amigcl)/5,
         identity= (in_simili+in_amsimb+in_acpier+in_acadop)/4,
         threat = as.numeric(in_amreal),
         ola=as.numeric(ola)
         )
# Hipotesis
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+dif_inm+nation_t1+cuestion_mig"

# E. Immigrants have Chilean friends 
amicl.null <- lmer(formula(paste0("in_amigcl~","1 + (1|idencuesta)+(1|comuna)")),data = df_study1)

amicl1 <- lmer(formula(paste0("in_amigcl~",h1,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
amicl2.ed <- lmer(formula(paste0("in_amigcl~",h2.educ,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
amicl2.in <- lmer(formula(paste0("in_amigcl~",h2.incom,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
amicl3 <- lmer(formula(paste0("in_amigcl~",h3,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
amicl4.kno <- lmer(formula(paste0("in_amigcl~",h4.know,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
amicl4.fri <- lmer(formula(paste0("in_amigcl~",h4.friend,"+(1|idencuesta)+(1|comuna)")),data = df_study1)

omit <- "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
texreg::knitreg(list(amicl1,amicl2.ed,amicl2.in,amicl3,amicl4.fri,amicl4.kno),
          omit.coef = omit)
```

## Conviviality (average)

```{r conviviality}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,in_simpat:edad,inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(conviviality=(in_ansied+in_simpat+in_valfam+in_valami+in_amigcl)/5,
         identity= (in_simili+in_amsimb+in_acpier+in_acadop)/4,
         threat = as.numeric(in_amreal),
         ola=as.numeric(ola)
         )

# Hipotesis
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+dif_inm+nation_t1+cuestion_mig"

# E. Immigrants have Chilean friends 
conv.null <- lmer(formula(paste0("conviviality~","1 + (1|idencuesta)+(1|comuna)")),data = df_study1)
conv1 <- lmer(formula(paste0("conviviality~",h1,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
conv2.ed <- lmer(formula(paste0("conviviality~",h2.educ,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
conv2.in <- lmer(formula(paste0("conviviality~",h2.incom,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
conv3 <- lmer(formula(paste0("conviviality~",h3,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
conv4.kno <- lmer(formula(paste0("conviviality~",h4.know,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
conv4.fri <- lmer(formula(paste0("conviviality~",h4.friend,"+(1|idencuesta)+(1|comuna)")),data = df_study1)

omit <- "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
texreg::knitreg(list(conv1,conv2.ed,conv2.in,conv3,conv4.fri,conv4.kno),
          omit.coef = omit)
```

## F. Similarity

```{r similarity}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,in_simpat:edad,inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(conviviality=(in_ansied+in_simpat+in_valfam+in_valami+in_amigcl)/5,
         identity= (in_simili+in_amsimb+in_acpier+in_acadop)/4,
         threat = as.numeric(in_amreal),
         ola=as.numeric(ola)
         )

# Hipotesis
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+dif_inm+nation_t1+cuestion_mig"

# F. Similarity  
simi.null <- lmer(formula(paste0("in_simili~","1 + (1|idencuesta)+(1|comuna)")),data = df_study1)

simi1 <- lmer(formula(paste0("in_simili~",h1,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
simi2.ed <- lmer(formula(paste0("in_simili~",h2.educ,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
simi2.in <- lmer(formula(paste0("in_simili~",h2.incom,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
simi3 <- lmer(formula(paste0("in_simili~",h3,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
simi4.kno <- lmer(formula(paste0("in_simili~",h4.know,"+(1|idencuesta)+(1|comuna)")),data = df_study1)
simi4.fri <- lmer(formula(paste0("in_simili~",h4.friend,"+(1|idencuesta)+(1|comuna)")),data = df_study1)

omit <- "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
texreg::knitreg(list(simi1,simi2.ed,simi2.in,simi3,simi4.fri,simi4.kno),
          omit.coef = omit)
```

## G. Loose identity

```{r loose-id}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

>>>>

---
title: "Analysis"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
      number_sections: yes
    code_folding: hide
    number_sections: yes
editor_options:
  chunk_output_type: console
---
# Setup

@@

```{css, echo=FALSE}
# /* expandir el espacio del documento*/
body .main-container {
      max-width: 2000px !important;
      width: 2000px !important;
    }
#/* expandir width de la TOC*/
div.tocify {
    width: 22% !important;
    max-width: 331px !important;
    max-height: 102% !important;
}
```

@@

```{r tab-desc, results="asis", warning=FALSE}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))
# Css
st_css()
st_options(lang = "en",
           footnote = NA,
           bootstrap.css = F,
           custom.css = here::here("input/css/dfsummary.css"),
           dfSummary.custom.1 = NA
           )

# Df variables nivel 1 __________________________________________________________
df_study1 <- 
  df_study_long_t5_comunas %>% 
  select(in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) 
lab_study1 <- sjlabelled::get_label(df_study1) 
df_study1 <- df_study1 %>% na.omit() %>% sjlabelled::set_label(lab_study1)

df<- dfSummary(x = df_study1,
               plain.ascii = FALSE,
               style = "grid",
               tmp.img.dir = "/tmp",
               graph.magnif = TRUE,
               headings = F,  # encabezado
               varnumbers = F, # num variable
               labels.col = T, # etiquetas
               na.col = F,    # missing
               graph.col = T, # plot
               valid.col = T, # n valido
               col.widths = c(700,10,10,10,10,10)
               )
# df$Variable <- NULL # delete variable column
view(df,
     file = here::here("output/tables/desc01.html")
     ) # Ver tabla en un archivo HTML
webshot::webshot(url =here::here("output/tables/desc01.html"),
        file =here::here("output/tables/desc01.png")) # Remover archivo HTML
# print(df, method = "render")
```

@@

```{r, results='asis'}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,
         in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(
    # conviviality=(in_ansied+in_simpat+in_valfam+in_valami+in_amigcl)/5,
         # identity= (in_simili+in_amsimb+in_acpier+in_acadop)/4,
         ola_f = ola,
         ola=as.numeric(ola),
         -in_amreal
         )

# Hypothesis___________________________________________________________________
h1.cat <- "ola_f+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"

hipotesis <- c(h1.cat,h1,h2.educ,h2.incom,h3,h4.know,h4.friend)
# Set the independent variables (IVs)
ivs<- df_study1 %>% select(starts_with("in_"),"conviviality","identity") %>% names()

# Create the object for each model
models <- list()
for (i in ivs) {
models[[i]] <- paste0(i,"~",hipotesis,"+(1|idencuesta)+(1|comuna)")  
}

# Estimate the multilevel models
fits <- list()
for (i in ivs) {
  for (z in models[[i]][1:length(hipotesis)]) {
    fits[[z]] <- lme4::lmer(formula = z, data = df_study1)
  }
}
fit1 <- fits
# change model names within list
names(fit1) <- paste0(rep(ivs,each=length(hipotesis)),1:length(hipotesis))

# Tables_______________________________________________________________________
omit <- "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
reorderc <- c(1:4,19,5:18,20:31) # the depends on the number of coeficients (!)
# detail for subsections:
# https://stackoverflow.com/questions/69338331/r-markdown-create-section-headers-in-r-and-print-r-output-in-same-section

cat(paste0("\n## ","A. Anxiety","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_ansied", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","B. Simpathy ","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_simpat", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","C. Family value migrant friends","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_valfam", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","D. Friend value migrant friends","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_valami", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","E. Immigrants have Chilean friends","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_amigcl", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","Conviviality (average)","\n"))

knitreg(l = fit1[names(fit1)[grepl("conviviality", names(fit1),"\n")]],
        omit.coef = omit,reorder.coef = reorderc)

#______________________________________________________________________________

cat(paste0("\n## ","F. Similarity","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_simili", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","G. Loose identity","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_amsimb", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","H. Immigrants keep customs","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_acpier", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","I. Adopt chilean customs","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_acadop", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","Identity (average)","\n"))

knitreg(l = fit1[names(fit1)[grepl("identity", names(fit1),"\n")]],
        omit.coef = omit,reorder.coef = reorderc)

#______________________________________________________________________________
cat(paste0("\n## ","J. Unemployment increases (Threat)","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_amreal", names(fit1),"\n")]],
        omit.coef = omit,reorder.coef = reorderc)
```
